The SMT Competition 2015--2018

### 2019-03-01 2018/report/SMT-COMP.tex
Minor (unique solutions)
Unique solutions: more correct numbers; use of parallelism

Solvers that rank highly in the competition-wide ranking
(Section~\ref{sec:floc}) often also solve many benchmarks uniquely,
but there are exceptions.  For instance, SMTInterpol has relatively
few unique solutions, despite achieving third place in the
competition-wide ranking in~2017 and~2018.  However, almost every
(sound) solver solves at least some benchmarks uniquely, and hence
contributes to the state-of-the-art.

@@

\begin{table}
  \caption{Number of main-track benchmarks uniquely solved by each
    solver (by year)}
  \label{table:unique-solutions}
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    Solver & 2015 & 2016 & 2017 & 2018 \\
    \midrule
    ABC               &       & 3     &       &        \\
    Alt-Ergo          &       &       &       & 1      \\
    AProVE            & 1     & 0     & 413   & 553    \\
    Boolector         & 37    & 23    & 97    & 62     \\
    COLIBRI           &       &       & 3     & 22     \\
    Ctrl-Ergo         &       &       &       & 12     \\
    CVC3              & 69    &       &       &        \\
    CVC4              & 4884  & 116   & 10258 & 100679 \\
    MapleSTP          &       & 2     &       &        \\
    {[}MathSAT{]}     & 13    & 28748 & 11    & 5      \\
    MinkeyRink        &       & 27    & 27    & 16     \\
    OpenSMT2          & 0     & 0     & 0     & 0      \\
    ProB              &       & 1     &       &        \\
    Q3B               &       & 0     & 89    & 0      \\
    raSAT             & 3     & 14    &       &        \\
    Redlog            &       &       & 4     &        \\
    SMT-RAT           & 13    & 0     & 85    & 2      \\
    SMTInterpol       & 2     & 2     & 5     & 4      \\
    SPASS-SATT        &       &       &       & 34     \\
    STP               & 4     & 2     & 4     & 5      \\
    toysmt            &       & 0     &       &        \\
    Vampire           &       & 139   & 753   & 652    \\
    veriT             & 5     & 21    & 55    & 57     \\
    XSat              &       &       & 0     &        \\
    Yices2            & 88    & 146   & 2379  & 1535   \\
    Z3                & 6139  & 242   & 40992 & 888    \\
    \midrule
    Total             & 11258 & 29486 & 55175 & 104527 \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

Solvers that rank highly in the competition-wide ranking
(Section~\ref{sec:floc}) often also solve many benchmarks uniquely,
but there are exceptions.  For instance, SMTInterpol has relatively
few unique solutions, despite achieving third place in the
competition-wide ranking in~2017 and~2018.  However, almost every
(sound) solver in the competition solves at least some benchmarks
uniquely, and hence contributes to the state-of-the-art.

@@

\begin{table}
  \caption{Number of main-track benchmarks uniquely solved by each
    solver (by year)}
  \label{table:unique-solutions}
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    Solver & 2015 & 2016 & 2017 & 2018 \\
    \midrule
    ABC               &       & 7     &       &        \\
    Alt-Ergo          &       &       &       & 1      \\
    AProVE            & 5     & 0     & 413   & 553    \\
    Boolector         & 37    & 25    & 97    & 62     \\
    COLIBRI           &       &       & 3     & 22     \\
    Ctrl-Ergo         &       &       &       & 12     \\
    CVC3              & 70    &       &       &        \\
    CVC4              & 4863  & 113   & 10258 & 100679 \\
    MapleSTP          &       & 0     &       &        \\
    {[}MathSAT{]}     & 21    & 28745 & 11    & 5      \\
    MinkeyRink        &       & 13    & 27    & 16     \\
    OpenSMT2          & 0     & 0     & 0     & 0      \\
    ProB              &       & 2     &       &        \\
    Q3B               &       & 0     & 89    & 0      \\
    raSAT             & 0     & 14    &       &        \\
    Redlog            &       &       & 4     &        \\
    SMT-RAT           & 12    & 0     & 85    & 2      \\
    SMTInterpol       & 1     & 1     & 5     & 4      \\
    SPASS-SATT        &       &       &       & 34     \\
    STP               & 4     & 1     & 4     & 5      \\
    toysmt            &       & 0     &       &        \\
    Vampire           &       & 130   & 753   & 652    \\
    veriT             & 7     & 19    & 55    & 57     \\
    XSat              &       &       & 0     &        \\
    Yices2            & 86    & 128   & 2379  & 1535   \\
    Z3                & 6118  & 244   & 40992 & 888    \\
    \midrule
    Total             & 11224 & 29442 & 55175 & 104527 \\
    \bottomrule
  \end{tabular}
\end{table}

\paragraph{Use of parallelism.}

It is evident both from the division rankings
(Section~\ref{sec:division-rankings}) and the competition-wide ranking
(Section~\ref{sec:floc}) that there is very little difference between
sequential and parallel performance.  Even though parallel solvers may
use up to four times as much CPU time, sequential and parallel
division winners are most often identical, as are sequential and
parallel scores for the competition-wide ranking.

%TODO: discuss whether this can be attributed to the hardness
%distribution of benchmarks (cf. VBS plot)

In Table~\ref{table:parallelism}, we report the quotient of CPU time
over wall-clock time (summed up over all main-track benchmarks) for
each solver, as well as for all solvers combined.  When there were
multiple versions of a solver (such as a sequential and a parallel
version), only the highest value is shown.  We note that this quotient
is close to~1 for most solvers: only about 4--8 main-track solvers
each year were participating with a version that made use of
parallelism.

\begin{table}
  \caption{Quotient of CPU time over wall-clock time for each
    main-track solver (by year).  Values below~1.1 are shown in gray.}
  \label{table:parallelism}
  \centering
  \begin{tabular}{lrrrr}
    \toprule
    Solver & 2015 & 2016 & 2017 & 2018 \\
    \midrule
    ABC               &     & \textcolor{gray}{1.0} &     &     \\
    Alt-Ergo          &     &     &     & 3.0 \\
    AProVE            & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{0.8} & \textcolor{gray}{0.8} \\
    Boolector         & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & 1.1 & 1.3 \\
    COLIBRI           &     &     & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} \\
    Ctrl-Ergo         &     &     &     & 4.0 \\
    CVC3              & \textcolor{gray}{1.0} &     &     &     \\
    CVC4              & 1.2 & 1.1 & 1.1 & \textcolor{gray}{1.0} \\
    MapleSTP          &     & 3.8 &     &     \\
    {[}MathSAT{]}     & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} \\
    MinkeyRink        &     & 3.6 & 2.0 & 3.9 \\
    OpenSMT2          & 3.7 & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} \\
    ProB              &     & \textcolor{gray}{1.0} &     &     \\
    Q3B               &     & 2.9 & 2.9 & 3.0 \\
    raSAT             & \textcolor{gray}{1.0} & 2.0 &     &     \\
    Redlog            &     &     & \textcolor{gray}{1.0} &     \\
    SMT-RAT           & 1.3 & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} \\
    SMTInterpol       & 1.4 & 1.1 & 1.1 & 1.1 \\
    SPASS-SATT        &     &     &     & \textcolor{gray}{1.0} \\
    STP               & \textcolor{gray}{1.0} & 3.6 & 3.8 & 3.8 \\
    toysmt            &     & \textcolor{gray}{1.0} &     &     \\
    Vampire           &     & 3.4 & 3.9 & 4.0 \\
    veriT             & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} \\
    XSat              &     &     & 1.8 &     \\
    Yices2            & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} \\
    Z3                & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} & \textcolor{gray}{1.0} \\
    \midrule
    All solvers       & 1.0 & 1.3 & 1.3 & 1.3 \\
    \bottomrule
  \end{tabular}
\end{table}
